\documentclass[../Main.tex]{subfiles}
\pagenumbering{roman}
\begin{document}
\begin{center}
    \Large{\textbf{ACKNOWLEDGMENTS}}\\
\end{center}
\vspace{1cm}

%Lời cảm ơn của sinh viên (SV) tới người yêu, gia đình, bạn bè, thầy cô, và chính bản thân mình vì đã chăm chỉ và quyết tâm thực hiện ĐATN để đạt kết quả tốt nhất, nên viết phần cảm ơn ngắn gọn, tránh dùng các từ sáo rỗng, giới hạn trong khoảng 100-150 từ.
I would like to express my profound appreciation to my family, friends and significant other for their unwavering support and patince throughout the process of writing my thesis. Their love, encouragement, and confidence in my abilities have been an inexhaustible source of fortitude and inspiration for me.\

Thank you for always being there for me, providing me with a nurturing enviroment, and teaching me the importance of perserverance and diligence. Your unconditional affection and encouragement have inspried me to pursue my academic objectives. \

Thank you for solid friendship and for being an unending source of motivation. During the difficult times of thesis writing, your presence, laughter, and words of encouragement have brought me pleasure and helped me maintain a healthy work-life balance.\

Lastly, i would like to express my sincerest gratitude to my supervisor, Ph.D. Thanh-Chung Dao. Your direction, expertise and commitment have been indispensable to my research and academic development. Your guidance has not only increased my expertise in the field, but has also inspired me to achieve new heights of intellectual inquiry. Even when the research appeared daunting, your perseverance, encouragement, and unwavering faith in my ability propelled me forward. I am extremely appreciative of the opportunities you have afforded me and the invalueable lessons I have gained under your direction. Thank you for being an outstanding mentor and for your unwavering support throughout the process of writing my thesis.





\end{document}
