\documentclass[../Main.tex]{subfiles}
\begin{document}
\begin{center}
    \Large{\textbf{ABSTRACT}}\\
\end{center}
\vspace{1cm}

The blockchain has emerged as a revolutionary technology with the potential to transform numerous industries by providing a decentralized and transparent platform for recording transactions and data securely. The administration of identities and authentication remains a significant challenge within the blockchain ecosystem, despite its many benefits. In order to resolve this issue, it is necessary to create software that bridges the gap between conventional web authentication methods and blockchain-based systems. This bridge software would facilitate a more user-friendly and accessible blockchain ecosystem, ensuring that users can access blockchain-based services and applications with seamless identity verification. Blockchain is renowned for its rigorous security features, and any software implementation must maintain this level of security while integrating with standard web authentication protocols. A failure to adequately resolve security concerns could undermine the trustworthiness of blockchain technology. Innovative approaches, such as Shamir's Secret Sharing (SSS)  and Distributed Key Generation (DKG), have considerable potential for addressing these issues. SSS is a cryptographic technique that divides a secret into multiple portions before distributing them to participants. This strategy ensures that no single entity has complete access to the secret, thereby enhancing security and reducing the likelihood of unauthorized access. DKG enables the collaborative generation of cryptographic keys without requiring a singular trusted party. This distributed method adds another layer of security and decentralization to the authentication procedure. I intend to develop a social authentication solution for decentralized applications (DApps) using SSS and DKG techniques. This solution would allow users to authenticate using their social network accounts while assuring their privacy and security through the use of secure and distributed authentication protocols. I will design the system architecture, implement the required software components, and assess the solution's performance and efficacy.
\begin{flushright}
Students\\
(Sign and full name)
\end{flushright}

\end{document}
